\documentclass[11 pt]{moderncv}

\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}

\moderncvtheme[blue]{classic}

\usepackage[utf8] {inputenc}

\usepackage{amsmath}

\usepackage[scale = 0.93]{geometry}
\setlength{\hintscolumnwidth} {2.35 cm}
\AtBeginDocument{\recomputelengths}

\firstname{Peter}
\familyname{Seger}
\mobile{503.544.6599}
\email{peterhseger@gmail.com}
\homepage{peterhenryseger.com}

\nopagenumbers{}
\begin{document}
\maketitle

\vspace{-.6in}

\section{Education}

\cventry{2016 - Present
Class of 2020
GPA: 3.91
}
{Franklin W. Olin College of Engineering}{}{Needham, MA}{}
{
	\textbf{Candidate for BS in Engineering: Concentration in Computer Engineering.}
	  Coursework includes:
    Modeling and Simulation of The World;
    Introduction to Sensors, Instrumentation, and Measurement;
    Software Design;
    Qualitative Engineering Analysis
	\newline
	\textit{Recipient of 4-year, 50\% Olin Merit Scholarship.}
}

\cventry{2012 - 2016
GPA: 3.82}{Valley Catholic High School}{}{Beaverton, OR}{}
{
	AP National Scholar with Honors; English \& French National Honor Society.
	\begin{flushright}
	\vspace {-0.3 in}
	\end{flushright}
	\vspace {-0.1 in}
}

\section{Experience}
\vspace{0.06 in}

\cventry{May 2017-
August 2017}
{Software Engineer Intern}
{Voss Technologies - Chalmers University}
{Gothenburg, Sweden}
{}
{
\begin{itemize}
	\item Worked in Sweden with professor building a design system for autonomous vehicles by building a schematic visualization system in \textbf{C}. 
	\item Used an existing API in Functional Language (FL) to recreate functionality in \textbf{C} to increase speed, accuracy, and dependability of the tool. 
	\item Used advanced \textbf{data structures and heuristics} to create informative and accurate schematics from Register Transfer Language (RTL) descriptions.
\end{itemize}
}


\cventry{Spring 2017}
{Barbot -  Project Manager}
{Olin College}
{}
{}
{
\begin{itemize}
	\item Project manager and system architect for a \textbf{Python} Flask webapp for automated parties. 
	\item Built a full stack webapp with \textbf{MySQL} database, \textbf{Bootstrap} front end, and \textbf{Flask} app development. 
	\item Worked to layout the system and describe all functionality and worked with three other team members with varying levels of experience to ensure everyone had impact. 
\end{itemize}
}

\cventry{Fall 2016 -Present}
{Firmware Lead - Formula SAE}
{Olin College}
{}
{}
{
\begin{itemize}
	\item Designing, laying out, and implementing a custom API in \textbf{C} to ensure other student team members build software that is safe, stable, and efficient for the car. 
	\item Also in charge of teaching all new members firmware skills such as Git, C, and AVR programming.
\end{itemize}
}

\cventry{Fall 2016 -Present}
{SLAC (Stay Late and Create)}
{Olin College}
{}
{}
{
\begin{itemize}
	\item Part of the leadership team for the club which promotes a collaborative work space to foster Olin's project based learning by holding weekly meetings with student-led workshops, corporate-led workshops, and snacks. 
	\item Work closely with corporate sponsors including Google, GE, Microsoft and others to secure funding for activities. 
\end{itemize}
}

\cventry{2014-Present}
{Sound Engineer}
{Freelance}
{Portland, OR}
{}
{
\begin{itemize}
	\item Self taught in the practice of live sound engineering including choosing equipment, setting it up, and running advanced shows. Engineered at music festivals, theatrical productions, and musicals including troubleshooting and organizing sound arrays. 
	\item Installed fulls sound systems including equipment, software, and training.
\end{itemize}
}

\cventry{2014-Present }
{Photographer}
{Peter Seger Photography}
{Portland, OR}
{}
{
\begin{itemize}
	\item Work freelance with focuses in portrait, landscape, and sports photography. Grew business to a profitable level.
	\item Published in editorial articles in The Oregonian covering a Fun Run. Portfolio at \href{www.petersegerphotography.com}{petersegerphotography.com}
\end{itemize}
}


\vspace{0.03 in}
\section{Projects \& Other Activities}

\cventry{September 2016-2017}
{Library Assistant}
{Olin College of Engineering}
{Needham, MA}
{}
{
\begin{itemize}
	\item Worked to design and manufacture a facade for the student run coffee shop on campus.
\end{itemize}
 }


\cventry{Fall 2016}
{Wanderer}
{MIT Media Lab Reality Virtually AR/VR Hackathon}
{}
{}
{
\begin{itemize}
	\item Worked in a team of five to create a VR experience for people with anxiety. Went in with no previous experience in Javascript, C\#, or Unity and created a bubbler feature using the newly release Google Daydream API to utilize the wand. More information can be found at \href{https://devpost.com/software/wanderers}{devpost.com/software/wanderers}
\end{itemize}
}

\section{Skills}

\cvline{}
{
\textbf{C},
\textbf{Python},
\textbf{Arduino},
\textbf{Java},
Flask,
MySQL,
\textbf{HTML},
MatLab,
Altium Designer,
\LaTeX{},
laser cutter,
mill,
ShopBot CNC Router.
}
\cvline{}
{Other: French language fluency \& conversational Swedish}

\end{document}