%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Uber} % Organization
    {San Francisco, CA} % Location
    {2018 \& 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Summer 2019 - \textit{Money Engineering Team}}
        \begin{itemize}
          \item {Lead the creation of a new tool used to maintain bank communication templates.}
          \item {Worked closely with stakeholders to determine requirements and use cases.}
          \item {Built webapp in \textbf{FusionJS} using \textbf{React} \& \textbf{Redux}.}
          \item {Held test session with users to ensure project was meeting their needs.}
        \end{itemize}
        \item {Summer 2018 - \textit{Customer Obsessions Team}}
        \begin{itemize}
          \item {Worked on predictive intent for ranking of help articles on help.uber.com.}
          \item {Designed and implemented a new backend service in \textbf{Go} for ingesting \textbf{Kafka} messages and interacting with \textbf{ML} models.}
          \item {Built multiple ETL pipelines for training ML models as well as included logging and metrics for services using ELK and Grafana.}
          \item {Project was used as a proof of concept for a larger initiative and this architecture is now being used for in-app help.}
        \end{itemize}
        %\item {New serivces included logging and metrics using ELK and Grafana. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Product Consultant} % Job title
    {Bigserene} % Organization
    {} % Location
    {Feb. 2019 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked with seed-stage startup to help define their product offering.
        \item Ensured product market fit by consulting with potential customers.
        \item Drafted list of product requirements to satisfy users' needs.
        \item Created mocks and built initial MVP app in \textbf{ReactJS} and \textbf{NodeJS}.
      \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Voss Technologies - Chalmers University} % Organization
    {Gothenburg, Sweden} % Location
    {May 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked in Sweden with professor building a design system for autonomous vehicles.
        \item Built a schematic visualization tool from an existing API to recreate functionality in \textbf{C} to increase speed, accuracy, and dependability. 
        \item Used advanced \textbf{data structures} and \textbf{heuristics} to create informative and accurate schematics from Register Transfer Language (RTL) descriptions.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Marketing Manager (Current) Firmware Lead (2017-2018)} % Job title
    {Olin Electric Motorsports (Olin College)} % Organization
    {Boston, MA} % Location
    {Sep. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked on designing, laying out, and implementing a custom API in \textbf{C} to ensure other student team members built software that is safe, stable, and efficient for the car. Also built new AVR buildchain using \textbf{Python}.
        \item Was in charge of teaching all new members firmware skills such as \textbf{Git}, \textbf{C}, and \textbf{AVR} programming.
        \item Currently in charge of securing ~\$50k in funds for the team through corportate sponsors and public/private grants.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
