%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CEO} % Role
    {TAE Furniture} % Title
    {Boston, MA} % Location
    {Aprl 2017 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built an online furniture business which designed and built folding furniture for small spaces.}
        \item {Focused on driving revenue and sales through different avenues such as online ads, local maker markets, and more.}
        \item {Handled all the banking, online store, and incorporation duties for the company.}
      \end{cvitems}
    }

  \cventry
  {Founder} % Role
  {Peter Seger Photography} % Title
  {} % Location
  {2014 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item Work freelance with focuses in portrait, landscape, and sports photography. Grew business to a profitable level.
	    \item Published in editorial articles in The Oregonian covering a Fun Run. Portfolio at \href{www.petersegerphotography.com}{petersegerphotography.com}
    \end{cvitems}
  }


  \cventry
  {Leadership Team Member} % Role
  {Stay Late and Create (SLAC)} % Title
  {Olin College} % Location
  {Fall 2016 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item Part of the leadership team for the club which promotes a collaborative work space to foster Olin's project based learning by holding weekly meetings with student-led workshops, corporate-led workshops, and snacks. 
	    \item Work closely with corporate sponsors including Google, GE, Microsoft and others to secure funding for activities.
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
